---
title: "Team Project 1"
author: "Anna Berman"
date: "10/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd('/Users/annaberman/Desktop/702 Modeling/Assignments/Team Project 1')
library(ggplot2)
library(dplyr)
library(gridExtra)
```

## Data Overview 

In the 1970s, researchers in the United States ran several randomized experiments intended to evaluate public policy programs. One of the most famous experiments is the National Supported Work Demonstration (NSWD), in which researchers wanted to assess whether or not job training for disadvantaged workers had an effect on their wages. Eligible workers were randomly assigned either to receive job training or not to receive job training. Since this is a randomized experiment, we can make causal claims about the effect of job training on wages for this population of workers. 

We analyze a subset of the data from the NSWD. These and other data were originally analyzed in a highly influential paper by the economist Robert Lalonde. The reference for the study is

Lalonde, R. J. (1986), Evaluating the econometric evaluations of training programs with experimental data, The American Economic Review, 76, 604 - 620.

```{r data}
# Load the data
lalonde <- read.csv('lalondedata.txt') %>%
    mutate(treat = as.factor(treat)) %>%
    mutate(treat = factor(treat, levels = c(0, 1)))
summary(lalonde)
```
 
## Exploratory Data Analysis

```{r explore, fig.height=8}
g1 <- ggplot(lalonde) +
    geom_boxplot(mapping = aes(x = treat, y = re74)) + 
    ylim(c(0,60000))
g2 <- ggplot(lalonde) +
    geom_boxplot(mapping = aes(x = treat, y = re75)) + 
    ylim(c(0,60000)) 
g3 <- ggplot(lalonde) +
    geom_boxplot(mapping = aes(x = treat, y = re78)) + 
    ylim(c(0,60000))
grid.arrange(g1, g2, g3,
             nrow = 2)
```

 